---
title: "RStudio Cheatsheet"
author: "Annette Hilton"
date: "2/11/2020"
output: html_document
toc: true
toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Attach necessary packages 

library(tidyverse)
library(here)
library(janitor)

```

# Introduction 

This is a RStudio cheatsheet designed to assist coders as a one-stop reference for basic RStudio functions. 

**Please note:** This document is a work in progress and may contain code that does not run in the cheatsheet. It is designed to be a quick reference, code may be copy/pasted from other projects; in the future, self-contained coding examples may be pursued. 

The cheatsheet is broken down into the following sections (Table of Contents):

- Set global options
- Helpful packages 
- Read in Data 
- Tidy data
- Sort data
  - Sort by column 
  - Create new column/modify column
  - Sort by row
- Saving Files/Graphs 
  - Save to specific pathway
  - Save file
  - Save graph
- Working with Dates
- Graphs/Visualization 
- Statistical Tests 
- Create new data
- Rmd Tips 
  - Insert a photo 
  - Tabs 
- Shiny Apps

# Cheatsheet Main 

## Set global options 

How to set global options for Rmd/Other 

```{r}
#---------------------------------------------------
# Set global options
#---------------------------------------------------

# In top code chunk: knitr::opts_chunk$set(echo = TRUE)

# Do not display messages 

message = FALSE 

# Do not display errors

error = FALSE 

# Do not display warnings 

warning = FALSE 

# No code in final output 

echo = FALSE 

# Disable scientific notation 

options(scipen=999)

```

## Helpful packages 

```{r}
#--------------------------------------------------
# Helpful Packages 
#--------------------------------------------------

library(tidyverse) # Most basic and helpful! 
library(janitor) # Helps with cleaning/data tidy 
library(here) # Specifies where a file is located

```


## Read in Data

Read in CSV or TSV files 

```{r}
#--------------------------------------------------
# Read in data (csv or tsv)
#--------------------------------------------------

# Read in csv 

readr::read_csv("file_name")

# Read in csv with specific file path 

readr::read_csv(here::here("folder_name", "file_name")) 

# Read in tsv 

readr::read_tsv("file_name")

```

Read in spatial data 

```{r}
#-------------------------------------------------
# Read in shapefile/spatial data 
#-------------------------------------------------

# Must have package `sf` installed 

read_sf(dsn = here::here("folder_name", "subfolder_name"), layer = "name_of_all_files_name" )

```


## Tidy Data

```{r}
#-------------------------------------------------
# Basic data tidying
#-------------------------------------------------

# Tidy column names to all lowercase (pipe into)

example_dataframe <- dataframe_original %>% 
clean_names() 

# Tidy rows/observations to lowercase 
# Overwrite column name with lowercase rows with `mutate()` and `str_to_lower()`

example_dataframe <- dataframe_original %>% 
  mutate(example_column_name = str_to_lower(example_column_name))

```


## Sort Data 
### Sort by column 
### Create new column/modify column 
### Sort by row 

```{r}

# Use `filter()` function 
# Note: Other `filter()` options exist, such as: 

filter_all()
filter_if()
filter_at()

# Filter by string pattern/text (keep)

example_dataframe <- dataframe_original %>% 
  filter(str_detect(example_column_name, pattern = "example_pattern"))

# Filter by string pattern/text (remove: !) 

example_dataframe <- dataframe_original %>% 
  filter(!str_detect(example_column_name, pattern = "example_pattern"))



```


## Saving Files/Graphs 

## Working with Dates

## Graphs/Visualization

## Statistical Tests 

## Create new data

## Rmd Tips 
### Insert photo
### Tabs 
### Table of contents 

## Shiny Apps 